Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-15 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex
Minor revisions in the figure description of Nikolaev2010

\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/Nikolaev2010-F2}
  \caption{
    \textbf{Distribution of $\beta_1$- and $\beta_2$-adrenergic receptors (AR) on the surface of cardiomyocytes obtained from healthy rats.}
    \textbf{a:} SICM image of a cardiomyocyte surface. The white arrows indicate the positions, where the stimulation of the $\beta_1$-AR was take place.
    \textbf{b:} F\"orster resonance energy transfer (FRET) YFP/CFP (yellow and cyan fluorescent protein) ratio after $\beta_1$-AR stimulation in the crest of the cell (a). 
    \textbf{c:} FRET YFP/CFP ratio after $\beta_1$-AR stimulation in the T-tubule of the cell (a).
    \textbf{d:} SICM image of a cardiomyocyte surface. The white arrows indicate the positions, where the stimulation of the $\beta_2$-AR was take place. 
    \textbf{e:} FRET YFP/CFP ratio after $\beta_2$-AR stimulation in the crest of the cell (c).
    \textbf{f:} FRET YFP/CFP ratio after $\beta_2$-AR stimulation in the T-tubule of the cell (c).
    ICI: ICI118551 is a $\beta_2$-AR antagonist; CGP: CGP20712A is a $\beta_1$-AR antagonist
    A decrease in the FRET YFP/CFP ratio between YFP and CFP indicates an increase in cAMP.
  }
  \label{fig:nikolaev2010}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/Nikolaev2010-F2}
  \caption{
    \textbf{Distribution of $\beta_1$- and $\beta_2$-adrenergic receptors (AR) on the surface of 
    cardiomyocytes obtained from healthy rats.}
    \textbf{a:} SICM image of a cardiomyocyte surface. The white arrows indicate the positions, 
    where the stimulation of the $\beta_1$-AR was take place.
    \textbf{b:} F\"orster resonance energy transfer (FRET)-YFP/CFP (yellow and cyan fluorescent 
    protein)-ratio after $\beta_1$-AR stimulation in the crest of the cell (a). 
    \textbf{c:} FRET-YFP/CFP-ratio after $\beta_1$-AR stimulation in the T-tubule of the cell (a).
    \textbf{d:} SICM image of a cardiomyocyte surface. The white arrows indicate the positions, 
    where the stimulation of the $\beta_2$-AR was take place. 
    \textbf{e:} FRET-YFP/CFP-ratio after $\beta_2$-AR stimulation in the crest of the cell (c).
    \textbf{f:} FRET-YFP/CFP-ratio after $\beta_2$-AR stimulation in the T-tubule of the cell (c).
    ICI: ICI118551 is a $\beta_2$-AR antagonist; CGP: CGP20712A is a $\beta_1$-AR antagonist
    A decrease in the FRET-YFP/CFP-ratio indicates an increase in cyclic adenosine monophosphate 
    (cAMP).
    % The rights need to be added here.
  }
  \label{fig:nikolaev2010}
\end{figure}
